\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 B  - Winter 2017}

\centerline{Final exam}

\centerline{Monday, March 13th, 2017}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 20 & \hspace{10mm} \hfill \\
\hline Problem 2 & 15 & \hspace{10mm} \hfill \\
\hline Problem 3 & 15 & \hspace{10mm} \hfill \\
\hline Problem 4 & 20  & \hspace{10mm} \hfill \\
\hline Problem 5 & 15  & \hspace{10mm} \hfill \\
\hline Problem 6 & 15  & \hspace{10mm} \hfill \\
\hline Total & 100 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 6 problems (7 pages) in this exam. Make sure you have them all. 
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.   

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 2 hours to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item (20 pts) Let $S$ be the cylinder $y^2+z^2 = 9$ for $-1 \leq x \leq 2$, oriented inward (i.e. toward the $x-$axis). Use Stokes' theorem to evaluate

\[
\iint_S \nabla \times \langle z^2, 0, 1+xy \rangle \, \cdot dS.
\]

Make sure to indicate how you are orienting the boundary curves. 

\vfill

\newpage \item (15 pts) Evaluate the surface integral

\[
\iint_S \langle 4xy, -2z, z^2 \rangle \, \cdot dS,
\]

where $S$ is the boundary of the hemisphere region $E = \{(x,y,z): x^2 + y^2 + z^2 \leq 25, y \leq 0 \}$, oriented inward, i.e. towards $E$. 

\vfill

\newpage \item (15 pts) Let $P$ be the ellipsoid defined by the equation $x^2 + \frac{y^2}{4} + z^2 = 1$. 

\begin{enumerate} \item (5 pts) Give a parameterization $r = r(\phi, \theta)$ of $P$ in terms of the angle coordinates $\phi$ and $\theta$ that we usually use for spherical coordinates.

\vspace{4cm}

\item (5 pts) Compute $r_\phi \times r_\theta$. 

\vfill

\item (5 pts) Find a vector that is normal to $P$ at the point $(x,y,z) = (1/4, \sqrt{3}, \sqrt{3}/4)$. 

\vfill

\end{enumerate}

\newpage \item (20 pts; 4 pts each) For each of the statements below, circle \textbf{True} if you think it is true and \textbf{False} if you think it is false. 

\begin{enumerate} \item \textbf{True}\hspace{5pt} \textbf{False} \hspace{5pt} Let $C$ be the curve $r(t) = \langle 2 + 3 \sin(2t), \cos^3(6t), 2 \cos(2 t) \rangle$ for $0 \leq t \leq \pi/2$. For any conservative vector field $F$,  

\[
\int_C F \, \cdot dr = 0.
\]

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} Let $S$ denote the surface of the sphere of radius $3$ centered at $(1,0, \sqrt{2})$, oriented outward. For any vector field $F$, 

\[ 
\iint_S \nabla \times F \, \cdot dS = 0.
\]

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} If $G$ is a vector field, and $\nabla \cdot G \neq 0$, then $G$ is not conservative. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} If $S$ is an oriented surface whose normal vector $n$ always has negative entries (i.e. $n \cdot \hat{i}, n \cdot \hat{j},$ and $n \cdot \hat{k}$ are always negative), then

\[
\iint_S \langle 1+\cos(x), y^2 + z^2, e^x  \rangle \, \cdot dS \leq 0.
\]

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} If $r(u,v)$ and $s(u,v)$ are any two parameterizations of the same surface $S$, over possibly different parameterization domains $D, D'$ in the $u$-$v$ plane, then 

\[ 
\iint_D (5u^2 - \sin(\pi u v)) |r_u \times r_v| dA = \iint_{D'} (5u^2 - \sin(\pi u v)) |s_u \times s_v| dA.
\]

\vfill


\end{enumerate}

%\newpage
%
%\item (20 pts) Let $E$ denote the unit cube in $\mathbb{R}^3$, $E = \{(x,y,z): 0 \leq x, y, z \leq 1\}$. Let $S = \partial E$ be the boundary of the cube, with the outward pointing orientation (away from $E$). Use the divergence theorem to evaluate 
%
%\[
%\iint_{\partial E} \langle 0, 0, e^{y+z} \rangle \cdot dS.
%\]

% \item (20 pts) Consider the radial vector field $F = \frac{1}{|r|^4} r$, where $r = \langle x, y, z \rangle.$ 
%
%\begin{enumerate} \item (5 pts) Find the divergence of $F$: write your final answer in terms of $r$. 
%
%\vfill
%
%\item (7 pts) Let $E_R$ be the spherical region $\{(\rho, \theta, \phi): 1 \leq \rho \leq R\}$, where $R > 1$ is a fixed number. Evaluate the volume integral
%
%\[
%\iiint_{E_R} \nabla \cdot F \, dV.
%\]
%
%\vfill
%
%\newpage
%
%\item (5 pts) Let $S_1$ denote the surface of the sphere of radius $1$ oriented toward the origin, and let $S_R$ denote the surface of the sphere of radius $R$ oriented away from the origin. According to the divergence theorem, 
%
%\[
%\iint_{S_1} F \cdot dS + \iint_{S_R} F \cdot dS = \iiint_{E_R} \nabla \cdot F \, \cdot dS.
%\]
%
%You found the value of the right hand side of this equation in part b: compute one of the integrals on the left hand side, and use your answer to find the value of the other integral. 
%
%\vfill 
%
%\item (3 pts) What happens to the values of the three integrals from part $c$ when $R \to \infty$?
%
%\vfill
%
%\end{enumerate}
%

\newpage

\item (15 pts) Consider the curve $C$ parameterized by $r(t) = \langle t^2, t, \ln(t) \rangle$ for $0 < t < 1$. Evaluate the line integral (with respect to arclength)

\[
\int_C x \sqrt{4e^{4z} + y^2 + 1} \, ds.
\]

\newpage

\item (15 pts) Let $D$ denote the unit square in $\mathbb{R}^2$, so $D = \{(x,y): 0 \leq x \leq 1, 0 \leq y \leq 1\}$. Consider the change of coordinates $x = u - v, y = uv$. 

\begin{enumerate} \item (8 pts) What region $R$ in the right half of the $u$-$v$ plane $\{(u,v): u \geq 0\}$ corresponds to $D$ under this transformation? Draw a picture of the image region, and explain how you know that $T(u,v) = \langle u - v, uv \rangle$ actually has domain $R$ and image $D$. 

\vspace{10cm}

\item (7 pts) Use the change of coordinates formula to re-write the double integral 

\[ 
\iint_D (x^2 + 4y^2) \, dA
\]

in $u-v$ coordinates, i.e. as an integral over the region $R$. Your answer should look like 

\[ 
\iint_R g(u,v) \, dA
\]

for some function $g$.  

\vfill

\end{enumerate}

\end{enumerate}


\end{document}
