\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 E}

\centerline{Final exam}

\centerline{Tuesday, December 10, 2019}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 12 & \hspace{10mm} \hfill \\
\hline Problem 2 & 12  & \hspace{10mm} \hfill \\
\hline Problem 3 & 12 & \hspace{10mm} \hfill \\
\hline Problem 4 & 12  & \hspace{10mm} \hfill \\
\hline Problem 5 & 12  & \hspace{10mm} \hfill \\
\hline Total & 60 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 5 questions on this exam. Make sure you have all five.
\item \textbf{You must show your work on all problems.}  The correct answer
with no supporting work may result in no credit. Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.
\item Give exact answers, and simplify as much as possible. 
\item Use the backs of pages \textit{for scratch work only}.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 110 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item Let $E$ be the region in $\mathbb{R}^3$ given by 

\begin{equation*}
E = \{(x,y,z):  x^2 + z^2 \leq y \leq 4 - x^2 - z^2 \text{ and } x > 0 \}.
\end{equation*}

Use the divergence theorem to evaluate the surface integral

$$\iint_{\partial E} \left( yz^2\hat{i} +x^2 y \hat{j} + \frac{1}{3}z^3 \hat{k} \right) \cdot d \bold{S},$$

where $\partial E$ denotes the boundary surface of $E$, oriented outward (normal points away from $E$). 
\newpage

\item Let $F = x^2 \hat{i} - xyz^2 \hat{j} + y^4 \hat{k}.$ 

\begin{enumerate} \item Find $\nabla \cdot F, \nabla \times F$, and grad$($div$(F))$.

\vfill

\item Is $F$ conservative? Why or why not?

\vfill 

\item Is grad$($div$(F))$ conservative? Why or why not?

\vfill

\item What is $\nabla \times (\nabla \times( \nabla \times (\nabla \times (\nabla \times F))))$? Explain your reasoning. 

\vfill

\end{enumerate} 
 
\newpage

\item Let $F = x \hat{i} - 2z \hat{j} + \hat{k}$, and let $S$ be the part of the plane $x - y + z = 3$ where $0 \leq y \leq 3$ and $-1 \leq z \leq 1$, oriented with the unit normal vector 

$$\hat{n} = \frac{1}{\sqrt{3}}\left(-\hat{i} + \hat{j} - \hat{k}\right).$$

Evaluate the surface integral 

\begin{equation*}
\iint_S F \cdot \, d\bold{S}.
\end{equation*}


\newpage

\item For each of the statements below, circle \textbf{True} if you think it is true, and circle \textbf{False} if you think it is false. You may use the space to do scratch work, but no partial credit will be awarded on this question. 

\begin{enumerate} 
\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} Suppose $F$ and $G$ are two vector fields such that 

$$\iint_S F \cdot \, d\bold{S} = \iint_S G \cdot \, d\bold{S}$$

where $S$ is the unit sphere, oriented outward. Then $F = G$ on $S$. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} If $H$ is a vector field satisfying $\nabla \cdot H = 0$, then 

$$\iint_S H \cdot \, d\bold{S} = 0$$

for any oriented surface $S$. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} $\nabla \cdot( \nabla f) = 0$ for any function $f: \mathbb{R}^3 \to \mathbb{R}$. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} If $F, G: \mathbb{R}^3 \to \mathbb{R}$ are vector fields satisfying $F \cdot \hat{k} = 0$ and $G \cdot \hat{k} = 0$, then 

$$(F \times G) \cdot \hat{i} = (F \times G) \cdot \hat{j} =  0.$$  

\vfill

\end{enumerate}

\newpage

\item Let $S$ be the bottom half of the unit sphere $x^2 + y^2 + z^2 = 1, z \leq 0$, oriented inward (normal points toward the origin). Also, let $C$ denote the boundary curve of $S$, i.e. the circle $x^2 + y^2 = 1$, oriented clockwise (when looking down from the positive $z$ axis). Use Stokes' theorem to evaluate the line integral

$$\int_C \left( 3y \hat{i} + x \hat{j} + 2x \hat{k} \right) \cdot  \, d\bold{r}.$$

\end{enumerate}

\end{document}
