\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 E  - Spring 2019}

\centerline{Midterm exam 2}

\centerline{Friday, May 24th, 2019}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 3 & \hspace{10mm} \hfill \\
\hline Problem 2 & 4 & \hspace{10mm} \hfill \\
\hline Problem 3 & 4 & \hspace{10mm} \hfill \\
\hline Problem 4 & 5 & \hspace{10mm} \hfill \\
\hline Problem 5 & 4 & \hspace{10mm} \hfill \\
\hline Total & 20 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 5 questions on this exam. Make sure you have all five.
\item \textbf{You must show your work on all problems.}  The correct answer
with no supporting work may result in no credit. Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.
\item Give exact answers, and simplify as much as possible. 
\item Use the backs of pages \textit{for scratch work only}.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item Let $f(x,y,z) = xz^2 - 2yz$. 

\begin{enumerate} \item[a)] Compute the directional derivative of $f$ at the point $(-1,0,2)$ in the direction $u = \frac{1}{\sqrt{3}} (\hat{i} + \hat{j} + \hat{k})$. 

\vfill 

\item[b)] What is the maximum value of directional derivative $D_u f(-1,0,2)$ as $u$ ranges over all unit vectors in $\mathbb{R}^3$? What is the unit vector $u$ for which the maximum is attained?

\vfill

\end{enumerate}

\newpage

\item For each pair of conservative vector field $F$ and curve $C$, first find a potential function for $F$, and then use the fundamental theorem of line integrals to evaluate $\int_C F \cdot dr$. 

\begin{enumerate} \item[a)] $F(x,y) = xy \hat{i} + \frac{1}{2}x^2 \hat{j}$, and $C$ is the part of the hyperbola $y = \frac{3}{x}$ between the points $(1,3)$ and $(3,1)$, traversed from left to right. 

\vfill

\item[b)] $F(x,y,z) = z\cos(x) \hat{i} - \hat{j} + \sin(x) \hat{k},$ and $C$ is the curve parameterized by $r(t) = (t, t, -1)$, for $0 \leq t \leq \pi/2$. 

\vfill

\end{enumerate}

\newpage


\item For each of the statements below, circle \textbf{True} if you think it is true, and circle \textbf{False} if you think it is false. You may use the space to do scratch work, but no partial credit will be awarded on this question. 

\begin{enumerate} 
\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} The function $f(x,y) = e^{x^2-2y^2}$ satisfies $\nabla f = 2x f(x,y) \hat{i} - 4y f(x,y)$.

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} The vector field $F = \frac{-y \hat{i} + x \hat{j}}{x^2+y^2}$ satisfies $\int_C F \cdot dr = 0$ where $C$ is the unit circle traversed counter clockwise. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} Let $G(x,y) = (9x + 2x^2 y^2) \hat{i} + x^3 y \hat{j}$. $G$ is a conservative vector field. 

\vfill

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{10pt} Let $F$ be a vector field defined on all of $\mathbb{R}^2$, and let $C$ be a curve starting at $(-3,1)$ and ending at $(2,2)$. Let $T$ denote the unit tangent vector field to $C$. Suppose that $F \cdot T < 0$ at every point on $C$. Then 

\[
\int_C F \cdot \, dr < 0.
\]

\vfill

\end{enumerate}

\newpage


\item Let $F(x,y) = 2x^2y \hat{i} - 3x \hat{j}$, and let $C$ denote the curve defined by the ellipse $x^2 + \frac{y^2}{9} = 1$, traversed clockwise. Use Green's theorem to evaluate $\int_C F \cdot dr$. 


\newpage

\item Let $f(x,y,z) = x^2 + z^2$, and consider the 3D region $E$ of points $(x,y,z)$ satisfying 

\[
z \geq 0 \text{ and } 4 \leq x^2+y^2+z^2 \leq 9 \text{ and } x^2 + y^2 \leq 4.
\]

Use cylindrical coordinates to set up the integral

\[
\iiint_E f \, dV.
\]

\textbf{You don't have to evaluate it.}


\end{enumerate}


\end{document}
