\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 D  - Winter 2018}

\centerline{Midterm exam 1}

\centerline{Friday, January 26, 2018}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 10 & \hspace{10mm} \hfill \\
\hline Problem 2 & 14 & \hspace{10mm} \hfill \\
\hline Problem 3 & 14 & \hspace{10mm} \hfill \\
\hline Problem 4 & 12  & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 problems on this exam. Make sure you have all four.
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.   

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage

\begin{enumerate}

\item (10 points) Consider the region $D = \{(x,y) \in \mathbb{R}^2: y \geq 1, x^2+y^2 \leq 4\}.$ Draw a picture of $D$, and evaluate

\[
\iint_D \frac{y^2}{x^2+y^2} \, dA.
\]

\newpage

\item (14 pts) Suppose there is a cylindrical can of beer occupying the region 

\[
\{(x,y,z) \in \mathbb{R}^3: y^2 + z^2 \leq 1, 0 \leq x \leq 4\}.
\]

A nervous freshman is swirling the can, concentrating the beer near the edge. Assume the beer has density function $f(x,y,z) = x^2 y^2$. Find the total volume of beer in the can by integrating $f$ over the region occupied by the can. 

\newpage

\item (14 points) Find the volume of the ``ice cream cone" region 

\[
E = \{(x,y,z) \in \mathbb{R}^3: x^2+y^2+z^2 \leq 1, z \geq 0, z^2 \geq x^2+y^2\}
\] 

using spherical coordinates. (No credit will be awarded for using any other coordinate system!)

\newpage


\item (12 pts) Consider the region $E$ bounded by the planes $z = 0, x = 0, x+2y+3z = 6$ and $y = z+1$. Paramaterize \textbf{but do not evaluate} the integral 

\[
\iiint_E xyz \, dV
\]

in the two orders given below. 

\begin{enumerate} \item (6 points) 

\begin{equation*}
 \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}}  \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}}  \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}} \rule{2cm}{.15mm} \, dx \, dy \, dz
\end{equation*}

\vfill

\item (6 points) 

\begin{equation*}
 \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}}  \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}}  \int_{\rule{1cm}{.15mm}}^{\rule{1cm}{.15mm}} \rule{2cm}{.15mm} \, dy \, dz \, dx
\end{equation*}
\vfill
\end{enumerate}



\end{enumerate}

\end{document}
