\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 A  - Spring 2017}

\centerline{Midterm exam 1}

\centerline{Friday, April 21, 2017}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 12 & \hspace{10mm} \hfill \\
\hline Problem 2 & 12  & \hspace{10mm} \hfill \\
\hline Problem 3 & 12 & \hspace{10mm} \hfill \\
\hline Problem 4 & 14  & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 questions on this exam. Make sure you have all four.
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.  

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item (12 pts) Let $R$ be the region in the $x$-$y$ plane given in polar coordinates as  

$$R = \{(r, \theta): \frac{1}{2} \csc \theta \leq r \leq \sin \theta, 0 \leq r < \infty, 0 \leq \theta \leq \pi\}.$$

Sketch the region $R$, and evaluate the double integral 

$$\iint_R \sin^2\theta \, dA.$$ 

\newpage

\item (12 pts) Let $D$ be the region in the $x$-$y$ plane bounded by the curves $y = x, y = 3x, y = 1/x$ and $y = 3/x$. Use the change of coordinates $x = u/v, y = v$ to evaluate the integral

\[ 
\iint_D xy \, dA.
\]
\newpage

\item[3.] (12 pts) Set up but \textbf{do not evaluate} the integral 
$$\iiint_E xz \, dV$$

in Cartesian coordinates, where $E$ is the solid (with finite volume) that lies in the first octant $x, y, z \geq 0$ and is bounded by the surfaces 

$$x=y^4, x=2y^2-1, z = 0 \text{ and } z=3y.$$

(For example, ``the surface $x=y^4$" means the set of all points $(x,y,z) \in \mathbb{R}^3$ satisfying $x=y^4$.)
\newpage

\item[4.] (14 pts) Professor Stella Artois wants to know how much beer her strangely shaped beer bottle can hold. The design is obtained by rotating the curve $x = 2+\cos \pi z, 0 \leq z \leq 5$ (in the $x$-$z$ plane) around the $z$ axis, and attaching caps at the top and bottom. Beer tends to be foamier at the top: the density of beer in the bottle is 

$$d(x, y, z) = \frac{6-z}{1+\frac{1}{2}\cos \pi z}.$$

Set up an integral to compute the mass of the beer in the bottle when it is full: that is, choose a coordinate system use it to and parameterize the integral

$$\iiint_E d(x,y,z) \, dV$$

where $E$ is the region inside the beer bottle. \textbf{You do not need to evaluate the integral.}




\end{enumerate}

\end{document}
