\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tikz}

\unitlength = .5cm 

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 A  - Summer 2017}

\centerline{Midterm exam 2}

\centerline{Friday, July 28th, 2017}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 10 & \hspace{10mm} \hfill \\
\hline Problem 2 & 15  & \hspace{10mm} \hfill \\
\hline Problem 3 & 10 & \hspace{10mm} \hfill \\
\hline Problem 4 & 15  & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 questions on this exam. Make sure you have all four.
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $3/4 + 1/2$
should be reduced to $5/4$.   

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 60 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item (10 pts) Let $f(x,y)$ be a function on $\mathbb{R}^2$. Assume that the minimum value of $D_u f(1,-3)$ is attained when $u = -\frac{\sqrt{2}}{2} \widehat{i} + \frac{\sqrt{2}}{2} \widehat{j}.$ Also, assume $\frac{\partial f}{\partial x}(1,-3) = +4$. 

\begin{enumerate} \item (5 pts) Find $\nabla f(1,-3)$. 

\vfill 

\item (2 pts) What unit vector $v$ maximizes $D_v f(1,-3)$?

\vfill 

\item (3 pts) Given your answer from part (a), is it possible that $f(x,y) = 10 - x^2 - 3xy + x$? Explain. 

\vfill 

\end{enumerate} 

\newpage

\item (15 pts) Let $D$ be the region in the plane under the parabola $y = 4-x^2$ and above the line $y = 3x$. 

\begin{enumerate} \item (3 pts) Draw $D$, and find the points where the two bounding curves meet. 

\vfill 

\item (7 pts) Consider the change of coordinates $u = x, v = y - 3x$. Draw the image of $D$ in the $u$-$v$ plane, and find the Jacobian of the transformation. 

\vfill 

\item (5 pts) Parameterize the double integral $\iint_D (x+y) \, dA$ in terms of $u$'s and $v$'s. \textbf{You do not need to evaluate it.}

\vfill 

\end{enumerate}

\newpage

\item (10 pts) Consider the vector field $F = 3x^2 y \widehat{i} + x^3 \widehat{j}$. 

\begin{enumerate} \item (5 pts) Is $F$ conservative? If so, find a potential function; if not, explain how you know it isn't conservative. 

\vfill 

\item (5 pts) Let $C$ be the curve consisting of the part of the circle $x^2 + y^2 = 1$ below the $x$-axis, from $(1,0)$ to $(-1,0)$, followed by the line segment from $(-1,0)$ to $(1,1)$. Evaluate $\int_C F \cdot \, dr$. 

\vfill 

\end{enumerate}

\newpage 

\item (15 pts) Let $R$ be the circle of radius $1$ centered at $(0,0)$, and let $C = \partial R$ be the boundary of $R$, oriented counter-clockwise. 

\begin{enumerate} \item (10 pts) Use Green's theorem to evaluate

\[
\int_C x^3 \, dy.
\]

\vfill 

\item (5 pts) Verify your answer from part $(a)$ by evaluating the line integral directly. 

\vfill 

\end{enumerate} 


\newpage 


\end{enumerate}

\end{document}
