\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 D  - Winter 2018}

\centerline{Midterm exam 2}

\centerline{Friday, February 16, 2017}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 15 & \hspace{10mm} \hfill \\
\hline Problem 2 & 13 & \hspace{10mm} \hfill \\
\hline Problem 3 & 11 & \hspace{10mm} \hfill \\
\hline Problem 4 & 11 & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 problems on this exam. Make sure you have all four.
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.   

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item (15 points) Let $f:\mathbb{R}^3 \to \mathbb{R}$ be a function with $f(1,0,1) = 2, \nabla f(1,0,1) = \langle 3, -2, 1 \rangle$, and $f(5,0,0) = 4, \nabla f(5,0,0) = \langle 1, 3, 0 \rangle.$  

\begin{enumerate} \item Let $G$ be the vector field defined by $G(x,y,z) = \nabla f(5,0,0)$ for all $(x,y,z) \in \mathbb{R}^3$. Is $G$ conservative? If so, give a potential function for $G$; if not, explain why. 

\vfill

\item Find $D_u f(1,0,1)$, where $u = \frac{1}{\sqrt{3}} \langle 1, 1, -1 \rangle.$

\vfill 

\item Consider the curve $C$ parameterized by $r(t) = (4t+1, t-t^2, 1-t^4)$ for $0 \leq t \leq 1$. What is $\int_C \nabla f \, \cdot dr$? (Make sure to justify your answer.)

\end{enumerate} 

\vfill

\newpage

\item (13 points) Consider the vector field $F = \langle x^2 y, -2x \rangle$, and let $C$ denote the part of the parabola $y = 1-x^2$ starting at $(-1,0)$ and ending at $(1,0)$. 

\begin{enumerate} \item Evaluate $\int_C F \cdot dr.$ 

\vfill 

\item Use the fundamental theorem for line integrals to evaluate the integral from part $(a)$, or explain why it cannot be applied. 

\vfill 

\end{enumerate}

\newpage


\item (11 points) Use the transformation $x = \frac{u}{v+1}, y = \frac{uv}{v+1}$ to set up the integral

\[
\iint_D (x+y) \, dA 
\]

in $u-v$ coordinates, where $D$ is the region in the $x-y$ plane bounded by the lines 

\[
y = 2x, y = x, y = 6-x, y = 3-x.
\]

Your integral should have explicit bounds in terms of $u$ and $v$, and the integrand should be a function of $u$'s and $v$'s. \emph{You do not need to evaluate the integral.}

\vfill 

\newpage


\item (11 points) Use Green's theorem to evaluate

\[
\int_C (y^2 \hat{i} + x^2 \hat{j}) \, \cdot dr,
\]

where $C$ is the boundary of the unit square $[0,1] \times [0,1]$, oriented counter-clockwise. 

\vfill


\end{enumerate}


\end{document}
