\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 B - Fall 2018}

\centerline{Midterm exam 1}

\centerline{Monday, October 22nd, 2018}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 12 & \hspace{10mm} \hfill \\
\hline Problem 2 & 12  & \hspace{10mm} \hfill \\
\hline Problem 3 & 12 & \hspace{10mm} \hfill \\
\hline Problem 4 & 14  & \hspace{10mm} \hfill \\
%\hline Problem 5 & 10 & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 questions on this exam. Make sure you have all four.
\item \textbf{You must show your work on all problems.}  The correct answer
with no supporting work may result in no credit. Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.  

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item \begin{enumerate} 

\item (12 points) Evaluate the integral 

\[
\iiint_E x \, dV,
\]

where $E$ is the region between the paraboloids $x = 8 - y^2 - z^2$ and $x = y^2 + z^2$. You should include a picture of $E$ or of any relevant cross section of $E$. 

\vfill
\end{enumerate}


\newpage


\item (12 points) Use spherical coordinates to evaluate the integral 

\[
\iiint_E y \, dV,
\]

where $E$ is the part of the unit sphere $x^2+y^2+z^2 \leq 1$ lying inside the octant $x,y,z \leq 0$. 

\vfill



%
%
%\newpage
%
%\item (10 pts) Let $D$ be the region in the $x$-$y$ plane bounded by the curves $y = \frac{x}{2}$ and $y^2 - 2y = x$. 
%
%\begin{enumerate} \item Draw a picture of $D$. 
%
%\vspace{4cm} 
%
%\item Write down a parameterization of $D$ in cartesian coordinates. 
%
%\vspace{3cm}
%
%\item Set up and evaluate the integral 
%
%\[
%\iint_D (y+1) \, dA
%\]
%
%using your parameterization from part $b$. 
%
%\end{enumerate}
%
%\vfill

\newpage

\item (12 points) Use the transformation $x = 2u + v, y = u + 2v$ to evaluate the integral

\[
\iint_T (x-2y) \, dA,
\]

where $T$ is the triangle in the $xy$ plane with vertices $(0,0), (2,1)$ and $(1,2)$. Draw pictures of $T$ and the transformed version of $T$ in the $uv$ plane. 

\vfill 


\newpage


\item (14 points) Consider the region $D \subset \mathbb{R}^2$ bounded by the curves $x,y \geq 0, x^2 + y^2 \leq 1$, and

\[
\left(x + \alpha \right)^2 + \left(y - \alpha \right)^2 \leq 2\alpha^2, \text{ where } \alpha = \frac{1 + \sqrt{3}}{2}.
\]

Draw a picture of $D$, and give a parameterization of $D$ in polar coordinates (i.e. describe $D$ as a set of $r$ and $\theta$ values). 

\medskip

\textit{Hint: the intersection of the two circles in the first quadrant occurs at $\theta = \pi/3$.}


%\item (12 pts) Consider the region in the $x$-$y$ plane inside the circle $x^2 + (y-1)^2 = 9$ and above the line $y = x \sqrt{3}$. 
%
%\begin{enumerate} \item Re-write the circle equation using polar coordinates. 
%
%\vspace{3cm}
%
%\item Solve the equation you got in part $a$ for $r$ as a function of $\theta$. 
%
%\vspace{5cm} 
%
%\item Draw a picture of $D$, and set up an integral in polar to find the area of $D$ using your answer from part $b$. \textbf{You do not need to evaluate it.} 
%
%
%\vfill 

\end{enumerate}

\end{document}
