\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 C - Spring 2019}

\centerline{Midterm exam 1}

\centerline{Friday, April 26, 2019}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 5 & \hspace{10mm} \hfill \\
\hline Problem 2 & 5  & \hspace{10mm} \hfill \\
\hline Problem 3 & 4 & \hspace{10mm} \hfill \\
\hline Problem 4 & 6  & \hspace{10mm} \hfill \\
%\hline Problem 5 & 10 & \hspace{10mm} \hfill \\
\hline Total & 2☻0 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 questions on this exam. Make sure you have all four.
\item \textbf{You must show your work on all problems.}  The correct answer
with no supporting work may result in no credit. Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.
\item Give exact answers, and simplify as much as possible. 
\item Use the backs of pages \textit{for scratch work only}.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item Consider the set of points $E \subset \mathbb{R}^3$ given by 

\[
E = \{(x,y,z): y^2 + z^2 \leq 4x^2 \text{ and } 0 \leq x \leq 1\}.
\]

\begin{enumerate} \item What do you get if you take a slice of $E$ in the plane $x = a$ for $a \in (0,1)$? (Describe the shape in words.)
\vspace{3cm} 

\item Find the surface area of $E$.

\vfill

\newpage

\item Find the volume of $E$.

\vfill
\end{enumerate}


\newpage

\item Let $D$ be the region in the $x$-$y$ plane bounded by the curves $y = \frac{x}{2}$ and $y^2 - 2y = x$. 

\begin{enumerate} \item Draw a picture of $D$. 

\vspace{4cm}  

\item Write down a parameterization of $D$ in cartesian coordinates. 

\vspace{3cm}

\item Set up and evaluate the integral 

\[
\iint_D \frac{1}{y} \, dA
\]

using your parameterization from part $b$. 

\end{enumerate}

\vfill





%
%
%\newpage
%
%\item (10 pts) Let $D$ be the region in the $x$-$y$ plane bounded by the curves $y = \frac{x}{2}$ and $y^2 - 2y = x$. 
%
%\begin{enumerate} \item Draw a picture of $D$. 
%
%\vspace{4cm} 
%
%\item Write down a parameterization of $D$ in cartesian coordinates. 
%
%\vspace{3cm}
%
%\item Set up and evaluate the integral 
%
%\[
%\iint_D (y+1) \, dA
%\]
%
%using your parameterization from part $b$. 
%
%\end{enumerate}
%
%\vfill

\newpage

\item Let $S$ denote the ball of radius $1$ centered about the point $(0,0,-1)$ in $\mathbb{R}^3$. Write down a parameterization of $S$ in spherical coordinates, and use it to evaluate the integral 

\[
\iiint_S z^2 \, dV.
\]


\newpage


\item Consider the tetrahedron $T \subset \mathbb{R}^3$ bounded by the planes $x = 0, z = 0, z = 2y$ and $2x + 2y + z = 4$. Set up the triple integral 

\[
\iiint_T xz \, dV
\]

with the two given orders of integration. \textbf{You do not need to evaluate the integrals.}

\begin{enumerate} \item $dx \,dy \,dz.$
\vfill


\item $dy \, dz \, dx.$
\vfill
\end{enumerate}


%\item (12 pts) Consider the region in the $x$-$y$ plane inside the circle $x^2 + (y-1)^2 = 9$ and above the line $y = x \sqrt{3}$. 
%
%\begin{enumerate} \item Re-write the circle equation using polar coordinates. 
%
%\vspace{3cm}
%
%\item Solve the equation you got in part $a$ for $r$ as a function of $\theta$. 
%
%\vspace{5cm} 
%
%\item Draw a picture of $D$, and set up an integral in polar to find the area of $D$ using your answer from part $b$. \textbf{You do not need to evaluate it.} 
%
%
%\vfill 

\end{enumerate}

\end{document}
