\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 324 B  - Winter 2017}

\centerline{Midterm exam 1}

\centerline{Friday, January 27, 2017}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 14 & \hspace{10mm} \hfill \\
\hline Problem 2 & 14 & \hspace{10mm} \hfill \\
\hline Problem 3 & 12 & \hspace{10mm} \hfill \\
\hline Problem 4 & 10  & \hspace{10mm} \hfill \\
\hline Total & 50 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 problems on this exam. Make sure you have all four.
\item You must show your work on all problems.  The correct answer
with no supporting work may result in no credit. \textbf{Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.} 
\item Give exact answers, and simplify as much as possible. 
For example, $\frac{\pi}{\sqrt{2}}$ is acceptable, but $\frac{1}{2} + \frac{3}{4}$
should be simplified to $\frac{5}{4}$.   

\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage
\begin{enumerate}

\item Let $C$ be the cone defined by $x^2 + y^2 \leq z^2 \leq R^2$, where $R > 0$ is a fixed number.

\begin{enumerate} \item (7 pts) Draw a picture of $C$, and find the volume of $C$. 

\vspace{4in} \item (7 pts) Recall that the surface area of a surface $S$ defined by $z = f(x,y)$ for $(x,y) \in D \subset \mathbb{R}^2$ is given by the double integral 

$$\iint_D \sqrt{1+\Bigl(\frac{df}{dx}\Bigr)^2 + \Bigl(\frac{df}{dy}\Bigr)^2 }dA.$$

Find the surface area of $C$ (including the base of the cone). 
\end{enumerate} 

\newpage

\item (14 pts) Use an appropriate change of coordinates to calculate the double integral 

$$\iint_D e^{8x^2+y^2} dA,$$

where $D$ is the interior of the ellipse $x^2 + (\frac{y}{2\sqrt{2}})^2 = 1$. 

\newpage

\item \begin{enumerate} \item (6 pts) Let $D$ be the region (with finite area) bounded by the curves $y = e^x$ and $y = e^{\sqrt{x}}$. Draw a picture of the region $D$, and use Cartesian coordinates to evaluate the double integral 

$$\iint_D \frac{1}{\ln(y)} dA.$$ 

\vfill \item (6 pts) Let $R = \{(x,y): (x-1)^2 + y^2 \leq 1 \textbf{ and } y \geq 0 \textbf{ and } x \geq 1\}$. Draw a picture of $R$, and use polar coordinates to evaluate the integral 

$$\iint_R \frac{x}{\sqrt{x^2+y^2}} dA.$$

You may use the fact that $\int \sec t$ $ dt = \ln\bigl|\sec t+\tan t\bigr| + C.$
\end{enumerate}

\vfill

\newpage





\item (10 pts) Let $E \subset \mathbb{R}^3$ consist of all points $(x,y,z)$ satisfying:

$$x^2 + y^2 + z^2 \leq 4,$$
$$0 \leq z \leq \sqrt{3} (x^2+y^2), \text{ and}$$
$$y \geq 0.$$

Consider the triple integral 

$$ \iiint_E \sqrt{\frac{x^2+y^2}{x^2+y^2+z^2}} dV.$$

\begin{enumerate} \item (5 pts) Parameterize the integral in spherical coordinates. \textbf{You do not need to evaluate it.} [Hint: you will need to figure out where the surfaces $x^2+y^2+z^2 = 4$ and $z = \sqrt{3} (x^2+y^2)$ intersect.]


\pagebreak

\item (5 pts) Set up the same integral using cylindrical coordinates. \textbf{You do not need to evaluate it.} 

\end{enumerate}


\end{enumerate}

\end{document}
