\documentclass[letterpaper]{article}

\usepackage{amsmath, amsfonts}
\usepackage{hyperref}
\usepackage{geometry}

\def\name{Jacob Richey}

\def\footerlink{}

\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {probability, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.6in, 8.5in},
  left=.90in,
  top=1.25in
}

\markright{\name}
\thispagestyle{empty}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\newenvironment{nobulletlist}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{https://www.renyi.hu}{Alfréd Rényi Institute of Mathematics} \\
  Budapest \\
  Reáltanoda utca 13-15, 1053 \\
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (+36) 30 1448 072 \\
    Email: & \href{mailto:jfrichey001@gmail.com}{\tt jfrichey001@gmail.com} \\
    Homepage: & \href{https://jfrichey.github.io/}{\tt Personal website} \\
  \end{tabular}
\end{minipage}

\vspace{1cm} 

\textbf{I am a postdoctoral fellow at the Rényi Institute in Budapest. My research field is combinatorial probability and statistics, including current projects related to: stochastic particle systems, random matrices, and mixing times for Markov chains.}

\section*{Employment}

\begin{itemize} 
  \item (2023-) Postdoctoral fellow, Alfréd Rényi Institute of Mathematics (Budapest, Hungary). \newline Faculty advisors: \href{https://math.bme.hu/~gabor/}{Gábor Pete}, \href{https://math.bme.hu/~rathb/}{Balázs Ráth}
  \item (2020-2023) Postdoctoral fellow, University of British Columbia (Vancouver, Canada). \newline Faculty advisors: \href{https://personal.math.ubc.ca/~angel/}{Omer Angel}, \href{https://personal.math.ubc.ca/~slade/}{Gordon Slade}.
\end{itemize}


\section*{Education}

\begin{itemize}

  \item (2014-2020) PhD Mathematics, University of Washington. \newline Advisor: \href{https://www.math.washington.edu/~hoffman/}{Christopher Hoffman}
  \item (2010-2014) B.A. Mathematics and Chinese Language, Dartmouth College. \newline Thesis advisor: \href{https://math.dartmouth.edu/~pw/}{Peter Winkler}. 
\end{itemize}

\section*{Papers}

\begin{center} {\textbf{Published}} \end{center}

\begin{enumerate}
	\item \href{https://projecteuclid.org/journals/electronic-journal-of-probability/volume-29/issue-none/Random-walks-on-regular-trees-can-not-be-slowed-down/10.1214/24-EJP1109.full}{\textit{Random walks on regular trees cannot be slowed down}}. Omer Angel, Jacob Richey, Yinon Spinka, Amir Yehudayoff. Electron. J. Probab. 29: 1-15 (2024). DOI: 10.1214/24-EJP1109 
	 

	  
	\item \href{https://link.springer.com/article/10.1007/s00220-022-04572-x}{\textit{Active phase for activated random walk on $\mathbb{Z}$}}. Chris Hoffman, Jacob Richey, Leonardo Rolla. Commun. Math. Phys. 399, 717–735 (2023). https://doi.org/10.1007/s00220-022-04572-x
	
		\item \href{https://www.cambridge.org/core/journals/journal-of-applied-probability/article/abs/intersections-of-random-sets/F94BF856EBE488909E2132C3BEBD0DDC}{\textit{Intersections of random sets.}} Jacob Richey, Amites Sarkar. Journal of Applied Probability. 2022;59(1):131-151. doi:10.1017/jpr.2021.34 
	   
	\item \href{https://ieeexplore.ieee.org/document/9187692}{\textit{Rumor source detection with multiple observations under adaptive diffusion protocols.}} Miklos Z. Racz, Jacob Richey. IEEE Transactions on Network Science and Engineering, vol. 8, no. 1, pp. 2-12, 1 Jan.-March 2021, doi: 10.1109/TNSE.2020.3022621
	    
 	\item \href{https://projecteuclid.org/journals/annales-de-linstitut-henri-poincare-probabilites-et-statistiques/volume-55/issue-3/Activated-random-walk-on-a-cycle/10.1214/18-AIHP918.full}{\textit{Activated random walk on a cycle}}. Riddhipratim Basu, Shirshendu Ganguly, Chris Hoffman, Jacob Richey. Ann. Inst. H. Poincaré Probab. Statist. 55(3): 1258-1277 (August 2019). DOI: 10.1214/18-AIHP918 
 
	\item \href{https://link.springer.com/article/10.1007/s10959-018-0808-2}{\textit{A smooth transition from Wishart to GOE}}. Miklos Racz, Jacob Richey. J Theor Probab 32, 898–906 (2019). https://doi.org/10.1007/s10959-018-0808-2
 \end{enumerate}
 
 \newpage
 
 \begin{center} {\textbf{Submitted}} \end{center}
 
\begin{enumerate}
	\item[7.] \href{https://arxiv.org/abs/2305.19333}{\textit{Diffusion-limited annihilating-coalescing systems}}. Sungwon Ahn, Matt Junge, Hanbaek Lyu, Lily Reeves, Jacob Richey, David Sivakoff. arXiv:2305.19333. Submitted to the Electronic Journal of Probability, 2023.
	\item[8.] \href{https://arxiv.org/abs/2212.08293}{\textit{Active phase for the Stochastic Sandpile on $\mathbb{Z}$}} Chris Hoffman, Yiping Hu, Jacob Richey, Douglas Rizzolo. arXiv:2212.08293. Submitted to Communications on Pure and Applied Mathematics, 2023.
 \end{enumerate}
 
 \begin{center} {\textbf{Arxiv Preprint}} \end{center}
 
 \begin{enumerate}
	\item[9.] \href{https://arxiv.org/abs/2409.09024}{\textit{Shifts of Finite Type Obtained by Forbidding a Single Pattern}}. Nishant Chandgotia, Brian Marcus, Jacob Richey, Chengyu Wu. arXiv:2409.09024 (September 2024).  
	\item[10.] \href{http://arxiv.org/abs/2409.19195}{\textit{Word length, bias, and bijections in Penney's ante}}. Matthew Drexel*, Peter Peng*, and Jacob Richey. *Undergraduate. arXiv: 2409.19195 (September 2024).
 \end{enumerate}
 
 \begin{center} {\textbf{Theses}}\end{center}

\begin{enumerate}
\item[11.] \href{https://math.dartmouth.edu/theses/undergrad/2014/Richey-thesis.pdf}{\textit{Counting clusters on a grid}}. Jacob Richey. Undergraduate honors thesis, Dartmouth College, 2014.

\end{enumerate}


\section*{Invited talks}
\begin{itemize}
 \item {\em{Hitting times and entropy for shifts of finite type}} (\href{https://jfrichey.github.io/pagedocs/sfttalk_halloween.pdf}{slides}) 
	\begin{itemize}
		\item Los Angeles probability forum, October `24
		\item Kutszem research seminar `24 (Rényi Institute, Budapest)
 		\item Rutgers combinatorics seminar `23
 		\item PIMS dynamics seminar `23 (UBC, Vancouver, Canada) 
	\end{itemize}
	
 \item {\em{Finding the source of a random diffusion.}} (\href{https://jfrichey.github.io/pagedocs/cornell_sourcefind.pdf}{slides}) 
 \begin{itemize} 
 	\item Cornell probability seminar `23
 	\item CUNY probability seminar `23
 	\item Dartmouth colloquium `21
 	\item University of Victoria probability seminar `21
\end{itemize}

 \item {\em{Phase transition for activated random walk and the stochastic sandpile}} (\href{https://jfrichey.github.io/pagedocs/kutszem_SSM_talk.pdf}{slides}) 
 \begin{itemize} 
	\item Ohio State University probability seminar, November `24
	\item University of Wisconsin Madison probability seminar, October `24
 	\item Kutszem research seminar `23 (Rényi Institute, Budapest)
 	\item University of Delaware probability seminar `23 
 	\item Cornell probability seminar `20
 	\item Random Structures and Algorithms `23 (Carnegie Mellon, Pittsburgh)
 	\item CRM Workshop `22 (Montreal)
 	\item AMS Special Session on Stochastic Spatial Models, JMM `20 (Denver)
 \end{itemize}
 
 \item {\em{Rumor source detection with multiple observations under adaptive diffusion protocols}} (\href{https://jfrichey.github.io/pagedocs/lednice_rumor.pdf}{slides}) 
 
 \begin{itemize} 
 	\item SIAM Workshop on Network Science `18 (Portland, OR)
 	\item Dynasnet Workshop `23 (Lednice, Czech Republic)
 \end{itemize}
 
 \item {\em{Phase transition for parking with coalescence}} 
 \begin{itemize} \item Northwest Probability Seminar `22. \end{itemize}
\end{itemize}

\section*{Undergraduate Teaching} 
\begin{itemize} \item (2020-2023) Lead instructor for courses in probability and calculus at the University of British Columbia. Class sizes ranged from 80 to 120. I was often in charge of one or two TAs/graders.  

\begin{itemize} \item MATH 302, Introduction to Probability. Quarters taught: Su23, W22, Su21
\item MATH 102, Differential Calculus with Applications to Life Sciences. W21. 
\item MATH 303, Introduction to Stochastic Processes. W20. 
\end{itemize} 

\item (2016-2020) Lead instructor for undergraduate courses in advanced multivariable calculus and linear algebra at the University of Washington. Class sizes ranged from 30 to 50. 
\begin{itemize} \item MATH 308, Matrix Algebra with Applications. Quarters taught: W20, Sp18.
\item MATH 324, Advanced Multivariable Calculus I. F19, Sp19, F18, W18, F17, Su17, Sp17, W17, Su16. 
\end{itemize} 

\item (2014-2016) Teaching assistant for courses in precalculus and calculus at the University of Washington. Led homework sections, usually two groups of 50 students, and helped with exam grading. 
\begin{itemize} \item MATH 120, Precalculus. Quarters taught: F16, Sp16, F15. 
\item MATH 111, Algebra with Applications. W15. 
\item MATH 112, Application of Calculus to Business and Economics. Sp15. 
\item MATH 125, Calculus with Analytic Geometry II. Su15, F14. 
\end{itemize} 
\end{itemize}

\section*{Teaching \& Outreach}

\begin{itemize} 
  \item (Spring, 2024) Taught a two-month-long minicourse on topics in large deviations at the Rényi Institute for graduate students, postdocs and faculty. 
  \item (September 2022) Volunteer at STEM Britannia science event for youth. Vancouver, BC.
    \item (2016-2021) Ran the advanced course at \href{https://www.math.washington.edu/~mathcircle/circle/}{UW Math Circle,} an NSF-supported math outreach program for advanced middle and high school students. Designed, tested, and taught new interactive lessons and activities in game theory, group theory, geometry, probability, and number theory. 
  \item (Summer, 2015) Junior staff at \href{http://www.hcssim.org/}{Hampshire College Summer Studies in Mathematics}. Led problem sessions, wrote and graded problem sets, taught a mini-course, and gave a `prime time' lecture. (Six days a week, 8 hours a day for 2 months.)
  \item (2012-2014) Private tutor for students in mathematics courses at Dartmouth College.

\end{itemize}


\section*{Undergraduate mentoring}

\begin{itemize}
  \item (2021-2023) Undergraduate Research Opportunities \href{https://www.uroubc.com/}{REX} at UBC. Mentor for two undergraduate research groups (three students each) in `21-22 and `22-23, culminating in a poster session. One project recently led to a submitted publication. Topics: street light percolation, coin bias in Penney's ante.
  
  \item (2015-2020) Washington Experimental Mathematics Lab (\href{https://www.wxml.math.washington.edu/}{WXML}). Co-led two undergraduate research projects, usually 3 or 4 students, over the course of a year or more, culminating in a poster presentation. Topics: statistics for random walks, randomness of the discrete logarithm. 

  \item (Summer, 2015) \href{https://www.math.washington.edu/~reu/index.html}{University of Washington Inverse Problems REU}. Gave a lecture at the REU colloquium, and advised an undergraduate student research project that resulted in a publication (\href{https://www.math.washington.edu/~reu/papers/2015/natalie/natalie.pdf}{link}). 

\end{itemize}

\section*{Organizing \& Service} 
\begin{itemize} 
  \item (2021-2023) Organizer, UBC probability seminar. Selected and coordinated speaker visits (some zoom), and maintained the seminar website (\href{https://secure.math.ubc.ca/Links/ProbSeminar/}{link}) and youtube page. 
  \item (2023-) Reviewer for MR reviews (9 articles total)
  \item Peer reviewer for: {\em{Journal of the London Mathematical Society}}, {\em{Electronic Journal of Probability}}, {\em{Stochastic Models}}  
  \end{itemize}

\section*{Conferences/visits}
\begin{itemize} \item Attended and presented a talk
\begin{itemize} 

 \item Random Structures and Algorithms, June 2023. Pittsburgh, PA
 \item Northwest Probability Seminar, October 2022. Seattle, WA
 \item CRM Workshop on Interacting Particle Systems and Hydrodynamic Limits, March 2022. Montreal, Canada
 \item JMM 2020. Denver, CO
 \end{itemize}
 
 \item Attended
 \begin{itemize}
 \item Saint-Flour Probability Summer School, July 2024. Saint-Flour, France
 \item Permutations and Probability (BIRS), September 2021. Banff, Canada

 \item AMS MRC on Stochastic Spatial Models, Summer 2019. Providence, RI
 \item Virginia Integrable Probability Summer School 2019. UVA, Charlottesville, VA
 \item Visitor at NYU Shanghai for two weeks in May 2019. Sponsor: Leonardo Rolla. Shanghai, China
 \item Northwestern Probability Summer School, 2018. Northwestern University, Evanston, IL
 \item Recent trends in Continuous and Discrete Probability, 2018. Georgia Tech, Atlanta, GA
\end{itemize}
\end{itemize}

\section*{Awards} 
\begin{itemize} 
 \item Gerald B. Folland Fellowship (2019)
\end{itemize}


\section*{Other}

\begin{itemize}
	\item US citizen, resident of New York City
	\item Languages: English, Mandarin Chinese 
	\item Programming languages: Python, Mathematica, Matlab, \LaTeX 
\end{itemize}

\bigskip


% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}