\documentclass[12 pt]{report}

\usepackage{epsfig}
\usepackage[in,empty]{myfullpage}
\usepackage{amssymb}
\usepackage{amsmath}

\baselineskip=20pt

\begin{document}

\noindent \vfill \noindent \large

\centerline{Math 308 O - Winter 2020}

\centerline{Midterm exam 1}

\centerline{Wednesday, January 29}

\normalsize

\vfill
\medskip
Name: \rule{10cm}{1pt}

\bigskip

\vfill
\begin{center}
{\large
\begin{tabular}{||c|c|r||}
\hline Problem 1 & 10 & \hspace{10mm} \hfill \\
\hline Problem 2 & 10 & \hspace{10mm} \hfill \\
\hline Problem 3 & 10 & \hspace{10mm} \hfill \\
\hline Problem 4 & 10 & \hspace{10mm} \hfill \\
\hline Total & 40 & \hspace{10mm} \hfill \\
\hline
\end{tabular}
}
\end{center}
\vfill
\begin{itemize}
\item There are 4 questions on this exam. Make sure you have all four.
\item \textbf{You must show your work on all problems.}  The correct answer
with no supporting work may result in no credit. Put a box
around your FINAL ANSWER for each problem and cross out any work
that you don't want to be graded.
\item Give exact answers, and simplify as much as possible. 
\item If you need more room, use the backs
of the pages and indicate to the grader that you have done so.
\item Raise your hand if you have a question.
\item Any student found engaging in academic misconduct will receive
a score of 0 on this exam.
\item You have 50 minutes to complete the exam.  Budget your time wisely! \\
\end{itemize}
\vfill
\begin{center}GOOD LUCK!\end{center}

\newpage

\begin{enumerate}

\item (10 points) Consider the vectors in $\mathbb{R}^3$ given by 


\[
u = \begin{bmatrix} 2 \\ 1 \\ -1 \\  \end{bmatrix}, \, v = \begin{bmatrix} 5 \\ 4 \\ -5 \end{bmatrix}, \, w = \begin{bmatrix} 3 \\ 0 \\ 1 \end{bmatrix}
\]

\begin{enumerate} \item Find all solutions $(x_1, x_2, x_3)$ to the system 

\begin{equation*} 
x_1 u + x_2 v + x_3 w = \begin{bmatrix} 0 \\ 0 \\ 0 \end{bmatrix}. 
\end{equation*}

\vfill

\item Is the set $\{u,v,w\}$ linearly dependent or independent? Explain. 

\vspace{150pt}

\end{enumerate}

\newpage

\item (10 points) \begin{enumerate} \item Give a matrix $A$ such that the linear transformation $T: \mathbb{R}^2 \to \mathbb{R}^2$ given by $T(v) = Av$ satisfies

\begin{equation*}
T\left(\begin{bmatrix} 1 \\ 0 \end{bmatrix}\right) = \begin{bmatrix} -1 \\ 3 \end{bmatrix} 
\end{equation*}

\vfill 

\item Suppose $u, v, w \in \mathbb{R}^4$ are vectors, and $x_1 = 3, x_2=-6, x_3= 1$ is a solution to the vector equation 

\begin{equation*}
x_1 u + x_2 v + x_3 w = \begin{bmatrix} 0 \\ 0 \\ 0 \\ 0 \end{bmatrix}.
\end{equation*}

Find another solution to this equation, other than $x_1 = x_2 = x_3 = 0$, or explain why there are no other solutions. 
\vfill
\end{enumerate} 

\newpage

\item (15 points) Circle \textbf{True} or \textbf{False} for each of the statements below. No justification is needed. 

\begin{enumerate} \item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} Let $v, w \in \mathbb{R}^3$ be any linearly independent vectors. Then the set $\{0, v, w\}$ is linearly independent (where $0$ represents the vector of all 0's).

\vfill 

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} Any four vectors in $\mathbb{R}^2$ are always linearly dependent. 

\vfill 

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} A system of linear equations always has 0, 1, or infinitely many solutions. 

\vfill 

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} Suppose $u, v, w \in \mathbb{R}^3$ are any vectors. Then the vector $u - v + 3w$ is in span$\{u,v,w\}$. 

\vfill 

\item \textbf{True} \hspace{5pt} \textbf{False} \hspace{5pt} There exist vectors $u, v, w \in \mathbb{R}^3$ such that $\{u,v\}$ is linearly dependent, and $\{u,v,w\}$ is linearly independent. 

\vfill 

\end{enumerate}

\newpage

\item (10 points) Find all values of $a$ such that span$\{u,v,w\} = $ span$\{u, v\}$, where 

\begin{equation*}
u = \begin{bmatrix} 1 \\ -2 \\ 1 \end{bmatrix}, \, v = \begin{bmatrix} 3 \\ 2 \\ -3 \end{bmatrix}, \, w = \begin{bmatrix} 2 \\ a \\ 5 \end{bmatrix}.
\end{equation*}

For those values of $a$, what is the span$\{u,v,w\}$: a point, a line, a plane, or all of $\mathbb{R}^3$?
\end{enumerate}

\end{document}
